---
title: "R/Business - Insurance Fraud Detection"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,   
                      message = FALSE,
                      warning = FALSE)
```

## R Business - Insurance Fraud Detection I

Our goal at R Business is to encourage the use of R Studio in a varity of industries where it's use has been underdevloped. One of these industries is insurance where Excle, VBA and SAS still seem to be the dominant forces. This tutorial is meant to show a simple example of what R Studio is capable of in an insurance related use case. Namely the detection of potential fraudulent activity. This is an extremely simplified data set and workflow, but the basic procedure remains the same even in more complex real world examples.

## Load Libraries

The first step is to load all the libraries you will need during this example

```{r, warning=FALSE}
# Load Libraries
library(dplyr)
library(readr)
library(randomForest)
library(rfUtilities)
library(rsample)
library(ggplot2)
library(caret)
library(e1071)
```

## Load Data

Then load the data

```{r data, echo=FALSE}
#Loading and Discovery

# Load Data
data <- read_csv("insurance_claims.csv")

# First Look at Data
head(data)
```


## Inspect Data


```{r data, echo=FALSE}
# Check Types
sapply(data, class)

# Check for NAs 
data[!complete.cases(data),] #non found

# Summarize Data
summary(data)
```

## Data Wrangling


```{r data, echo=FALSE}
#Data Wrangling
data$fraud_reported[data$fraud_reported == 'Y']  <- 1
data$fraud_reported[data$fraud_reported == 'N']  <- 0
data$fraud_reported <- as.integer(data$fraud_reported)
data$insured_zip <- as.character(data$insured_zip)
data$policy_bind_date <- as.Date(data$policy_bind_date, format = '%m/%d/%y')

# Check for amount of uniqe values
sapply(sapply(data, unique), length)
```
# Prepare Data for RF

```{r data, echo=FALSE}
# Drop obvious colimns
drops <- c('incident_location','policy_bind_date','incident_date','insured_occupation','insured_zip', 'policy_number')
data <- data[ , !(names(data) %in% drops)]

# turn into factors
data <- data %>% mutate_if(is.character, as.factor)
data$fraud_reported <- as.factor(data$fraud_reported)
```

## Split Data

```{r data, echo=FALSE}

# For reproducability
set.seed(52)

# Split Data
data_split <- initial_split(data, prop = .7)
data_train <- training(data_split)
data_test  <- testing(data_split )
```

## Basic Implementation & Analysis

```{r data, echo=FALSE}
# Basic Implementation & Analysis

# default RF model
rf1 <- randomForest(
  formula = fraud_reported ~ .,
  data    = data_train)

# Model
rf1
```

# Check Results

```{r data, echo=FALSE}
# Plot tree
plot(rf1)

# Lowest MSE
which.min(rf1$mse)

# RMSE of this optimal random forest
# sqrt(rf1$mse[which.min(rf1$mse)])

#Variable Importance
rf1$importance
```

## RF Initial Validation


```{r data, echo=FALSE}
# Split down set further for validation set on training data

# create training and validation data 
data_split <- initial_split(data_train, .8)

# training data
data_train_v2 <- analysis(data_split)

# validation data
data_valid <- assessment(data_split)
x_test <- data_valid[setdiff(names(data_valid),"fraud_reported")]
y_test <- data_valid$fraud_reported

rf_oob_comp <- randomForest(
  formula = fraud_reported ~ .,
  data    = data_train_v2,
  xtest   = x_test,
  ytest   = y_test)

# extract OOB & validation errors
oob <- sqrt(rf_oob_comp$mse)
validation <- sqrt(rf_oob_comp$test$mse)

# compare error rates
tibble::tibble(
  `Out of Bag Error` = oob,
  `Test error` = validation,
  ntrees = 1:rf_oob_comp$ntree
) %>%
  gather(Metric, RMSE, -ntrees) %>%
  ggplot(aes(ntrees, RMSE, color = Metric)) +
  geom_line() +
  scale_y_continuous(labels = scales::dollar) +
  xlab("Number of trees")

```



## RF Tuning

```{r data, echo=FALSE}
# names of features
features <- setdiff(names(data_valid),"fraud_reported")

# tune Random Forest
rf2 <- tuneRF(
  x          = data_train[features],
  y          = data_train$fraud_reported,
  ntreeTry   = 500,
  mtryStart  = 5,
  stepFactor = 1.5,
  improve    = 0.01,
  trace      = TRUE      # to not show real-time progress 
)

# Try best version
rf2 <- randomForest(
  x          = data_train[features],
  y          = data_train$fraud_reported,
  data    = data_train,
  ntree = 500,
  mtry = 15
)
```


# Check results


```{r data, echo=FALSE}
rf2

# Plot tree
plot(rf2)

#Variable Importance
rf2$importance
```


## Predicting

```{r data, echo=FALSE}
# randomForest
pred_randomForest <- predict(rf2, data_test)
head(pred_randomForest)

# Make pred column
data_test$pred <- predict(rf2, data_test)
data_test$pred_final <- as.integer(ifelse(data_test$pred > 0.3 ,1 ,0))
                          
# Confusion Matrix
confusionMatrix(as.factor(data_test$fraud_reported), as.factor(data_test$pred_final))
```



